
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# sealr 

[![Build Status](https://travis-ci.org/jandix/sealr.svg?branch=master)](https://travis-ci.org/jandix/sealr)

The goal of sealr is to provide multiple authentication and authorization strategies for [plumber](https://www.rplumber.io/) by using [filters](https://www.rplumber.io/docs/routing-and-input.html#filters). In doing so, we hope to make best practices in authentication easy to implement for the R community.
The package is inspired by the amazing [passport.js](http://www.passportjs.org/) library for Node.js.

## Disclaimer
`r emo::ji("warning")` We are currently looking for security experts to help us develop this project / review our code. That being said, while we try to thouroughly understand the concepts behind a strategy before we implement it in *sealr*, **we are not experts** in security. Please make sure you understand the risks and possible attack vectors when using *sealr* - especially in  production environments. `r emo::ji("warning")`

## Installation

Currently, the package is under development. Please feel free to contribute to the package. You can install and use the package using `devtools`. 

```{r installation, eval=FALSE}
devtools::install_github("jandix/sealr")
```

## Contribute

We are still at the very beginning of the package and we welcome any support and contribution. Comment on an existing issue
or file a new one on [GitHub](https://github.com/jandix/sealr/issues). 

## Testing
You can use curl for testing purposes. Unfortunately, curl quickly gets quite complicated if you want to add a body, parameters and unique headers. Therefore, we recommend to use [Postman](https://www.getpostman.com/) for larger, more complicated projects. 

## Examples
We provide some simple sample implementations for different strategies and use cases. 
You can find them on the subpages of the different strategies in the navigation bar on the left. 

## Warranity Notice

THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE SOFTWARE.


## Plumber filters for authentication / authorization
The primary logic of *sealr* is based on plumber filters (although you can use sealr functionality 
without filters as well by using the `is_authed` functions directly, see below). 
"Plumber filters can be used to define a “pipeline” for handling incoming requests" ([Plumber docs](https://www.rplumber.io/docs/routing-and-input.html#filters)). 

So if your plumber API receives a request, the request will first be routed through the different filters before 
it "arrives" at its destination endpoint. 

The idea of *sealr* is to use a filter for authentication. If a request is not properly authenticated / authorized, *sealr* will immediately return a "401 - Authentication failed." error from the filter to the user. In this way, 
an unauthenticated / unauthorized request will not "reach" its destination endpoint. 


## authenticate
*sealr*'s main function is the `authenticate` function. It is supposed to be used within a plumber filter. `authenticate` takes a
`is_authed_*` function (see below) as input and depending on the output of this "checker" function, 
takes action:

- if the request is authenticated / authorized, it forwards to the next plumber handler using `plumber::forward`. 
- if the request is not authenticated / authorized, it `return`s to the user, passing forward HTTP status code, description and message from the output of the `is_authed_` function. Most often, this will be a "401 - Authentication failed." error.

By accepting a function object as argument, `authenticate` is quite flexible: You can even pass your own `is_authed` function. See the examples section of `?sealr::authenticate` for a simple example. 

## is_authed functions
The functions starting with `is_authed` provide the actual implementations of the 
different authentication / authorization strategies that *sealr* aims to provide.
Currently implemented are:

- `is_authed_jwt`: implements JSON Web Token verification and checking. 
- `is_authed_oauth2_google`: implements Google's OpenID Connect (which is based on OAuth2.0)

`is_authed_*` functions return a list with the following elements:

- `is_authed`: TRUE or FALSE. Result of the check whether the request is authenticated / authorized. 
- `status`: character. Optional (typically only set if `is_authed` is FALSE). Short description of HTTP status code.
- `code`: integer. Optional (typically only set if `is_authed` is FALSE). HTTP status code.
- `message`: character. Optional (typically only set if `is_authed` is FALSE). Longer description.

Usage of the `is_authed` functions is not restricted to plumber filters. For example, 
you can use an `is_authed` function at the top of an endpoint to restrict access to certain endpoints or use
different authorization "levels" for different endpoints. This is particularly relevant if you have more than two "levels" of authorization (see the [claims example](https://jandix.github.io/sealr/docs/jwt/jwt_claims_example/)). 

