---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# JWT Claims Example 
JSON Web Tokens (JWT) *can* contain claims. "Claims are statements about an entity (typically, the user) and additional data" ([https://jwt.io/introduction/](https://jwt.io/introduction/)). They are expressed as key-value pairs.

There are three different types of claims: registered, public and private claims. All types of claims are implemented in the same manner, they only differ in whether and where the claims are registered with the Internet Assigned Numbers Authority (IANA). For example, the `iss` claim is a registered claim defined in the JWT standard [RFC 7519](https://tools.ietf.org/html/rfc7519#page-8) and registered at IANA. See the [JWT Introduction](https://jwt.io/introduction/) of [jwt.io](jwt.io) for more details.

`sealr` allows you to check for the validity of all types of claims in a given JWT using the `claims` argument of the `sealr::jwt` function. 

In this example implementation, we have two filters:

The filter `sealr-jwt` simply checks whether the user is authenticated and that the issuer claim `iss` is set to `mygreatplumberapi`, the value we set in the `authenticate` route.
The second filter  `sealr-jwt-admin-only` additionally checks whether the user is an admin by validating that the claim `admin` is `TRUE`. 

```{r eval=FALSE}
# integrate the jwt strategy in a filter
pr$filter("sealr-jwt", function (req, res) {
  # simply call the strategy and forward the request and response
  sealr::jwt(req = req, res = res, secret = secret,
             claims = list(iss = "mygreatplumberapi"))
})

pr$filter("sealr-jwt-admin-only", function (req, res) {
  # simply call the strategy and forward the request and response
  sealr::jwt(req = req, res = res, secret = secret,
             claims = list(iss = "mygreatplumberapi", admin = TRUE))
})

```


We now have two levels of access using filters: routes that are open to all authenticated users with a JWT issued by `mygreatplumberapi` and routes that are accessible to admins only. The former requires `preempt`ing the more restrictive `sealr-jwt-admin-only` filter. 

Unfortunately, it is currently not possible to extend this filter-based authorization mechanism to more than two authorization "levels" because `plumber` does not allow for preempting more than one filter per route. 

## Install the packages
Install the following packages if you haven't already:

- sealr
- httr
- jose
- jsonlite

## Run plumber

Source `jwt_claims_example.R` in your R session. This will make the API available at `localhost:9090`.

## Make some requests 

### Authentication route 

Using curl, Postman or a similar tool for sending HTTP requests, send a POST request with the details of one of the two users that are in the API's "database" (in this simplified example, a data frame).


```{r echo=FALSE}
# define a user database
# you should probably use a SQL database instead of data frames
users <- data.frame(id       = integer(),
                    name     = character(),
                    password = character(),
                    admin = logical(),
                    gender = character(),
                    stringsAsFactors = FALSE)

# create test user
users <- rbind(users, data.frame(id       = 1,
                                 user     = "jane@example.com",
                                 password = bcrypt::hashpw("12345"),
                                 admin = TRUE,
                                 gender = "woman",
                                 stringsAsFactors = FALSE))
users <- rbind(users, data.frame(id       = 2,
                                 user     = "bob@example.com",
                                 password = bcrypt::hashpw("45678"),
                                 admin = FALSE,
                                 gender = "man",
                                 stringsAsFactors = FALSE))

kableExtra::kable(users, format = "markdown")
```

Get the JWT for both users: 

- Jane 

```
curl --data '{"user": "jane@example.com", "password": "12345"}' localhost:9090/authentication
["eyJ0eXAiOiJKV1QiLCJhbGciOiJIUzI1NiJ9.eyJpc3MiOiJteWdyZWF0cGx1bWJlcmFwaSIsImlhdCI6MTU1MjU2NjAzNSwiYWRtaW4iOnRydWUsImdlbmRlciI6IndvbWFuIiwidXNlcklEIjoxfQ.jNSnrZl3_a3iLsfOuJCB0dIvOOgvpZFXC_v48Odh43A"]
```

- Bob 

```
curl --data '{"user": "bob@example.com", "password": "45678"}' localhost:9090/authentication
["eyJ0eXAiOiJKV1QiLCJhbGciOiJIUzI1NiJ9.eyJpc3MiOiJteWdyZWF0cGx1bWJlcmFwaSIsImlhdCI6MTU1MjU2NjE1MSwiYWRtaW4iOmZhbHNlLCJnZW5kZXIiOiJtYW4iLCJ1c2VySUQiOjJ9.rPgUcU3m7P8dhWRYKzMVUFqVH2zdzfgQxpPp6j54ZOE"]
```

### Routes with different authorization levels

Both users can access the `/secret` route because they both have valid JWT issued by `mygreatplumberapi`. The route `preempt`s the more restrictive `sealr-jwt-admin-only` filter so even non-admin Bob has access.

- Jane
```
curl -H "Authorization: Bearer eyJ0eXAiOiJKV1QiLCJhbGciOiJIUzI1NiJ9.eyJpc3MiOiJteWdyZWF0cGx1bWJlcmFwaSIsImlhdCI6MTU1MjU2NjAzNSwiYWRtaW4iOnRydWUsImdlbmRlciI6IndvbWFuIiwidXNlcklEIjoxfQ.jNSnrZl3_a3iLsfOuJCB0dIvOOgvpZFXC_v48Odh43A" localhost:9090/secret

["Access to route that requires authentication was successful."]
```

- Bob
```
curl -H "Authorization: Bearer eyJ0eXAiOiJKV1QiLCJhbGciOiJIUzI1NiJ9.eyJpc3MiOiJteWdyZWF0cGx1bWJlcmFwaSIsImlhdCI6MTU1MjU2NjE1MSwiYWRtaW4iOmZhbHNlLCJnZW5kZXIiOiJtYW4iLCJ1c2VySUQiOjJ9.rPgUcU3m7P8dhWRYKzMVUFqVH2zdzfgQxpPp6j54ZOE" localhost:9090/secret

["Access to route that requires authentication was successful."]
```

In contrast, only Jane can access the `/secret-admin-only` route.

- Jane
```
curl -H "Authorization: Bearer eyJ0eXAiOiJKV1QiLCJhbGciOiJIUzI1NiJ9.eyJpc3MiOiJteWdyZWF0cGx1bWJlcmFwaSIsImlhdCI6MTU1MjU2NjAzNSwiYWRtaW4iOnRydWUsImdlbmRlciI6IndvbWFuIiwidXNlcklEIjoxfQ.jNSnrZl3_a3iLsfOuJCB0dIvOOgvpZFXC_v48Odh43A" localhost:9090/secret-admin-only

["Access to route that requires admin authorization was successful."]
```

- Bob 
```
curl -H "Authorization: Bearer eyJ0eXAiOiJKV1QiLCJhbGciOiJIUzI1NiJ9.eyJpc3MiOiJteWdyZWF0cGx1bWJlcmFwaSIsImlhdCI6MTU1MjU2NjE1MSwiYWRtaW4iOmZhbHNlLCJnZW5kZXIiOiJtYW4iLCJ1c2VySUQiOjJ9.rPgUcU3m7P8dhWRYKzMVUFqVH2zdzfgQxpPp6j54ZOE" localhost:9090/secret-admin-only

{"status":["Failed."],"code":[401],"message":["Authentication required."]}
```
