---
output: 
  md_document:
    preserve_yaml: true
title: sealr
weight: 1
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


[![Build Status](https://travis-ci.org/jandix/sealr.svg?branch=master)](https://travis-ci.org/jandix/sealr)
[![codecov](https://codecov.io/gh/jandix/sealr/branch/master/graph/badge.svg)](https://codecov.io/gh/jandix/sealr)


The goal of sealr is to provide multiple authentication and authorization strategies for [plumber](https://www.rplumber.io/) by using [filters](https://www.rplumber.io/docs/routing-and-input.html#filters). In doing so, we hope to make best practices in authentication easy to implement for the R community.
The package is inspired by the amazing [passport.js](http://www.passportjs.org/) library for Node.js.

## Plumber filters for authentication / authorization
coming soon

## Implementation overview
#### authenticate
`sealr`'s main function is the `authenticate` function. `authenticate` takes a
`is_authed_*` function (see below) as input and depending on the output of this "checker" function, 
takes action:

- if the request is authenticated / authorized, it forwards to the next plumber handler using `plumber::forward`. 
- if the request is not authenticated / authorized, it `return`s to the user, passing forward HTTP status code, description and message from the output of the `is_authed_` function. 

By accepting a function object as argument, `authenticate` is quite flexible: You can even pass your own `is_authed` function. 

#### is_authed functions
The functions starting with `is_authed` provide the actual implementations of the 
different authentication / authorization strategies that `sealr` aims to provide.
Currently implemented are:

- `is_authed_jwt`: implements JSON Web Token verification and checking. 
- `is_authed_oauth2_google`: implements Google's OpenID Connect (which is based on OAuth2.0)

`is_authed_*` functions return a list with the following elements:

- `is_authed`: TRUE or FALSE. Result of the check whether the request is authenticated / authorized. 
- `status`: character. Optional (typically only set if `is_authed` is FALSE). Short description of HTTP status code.
- `code`: integer. Optional (typically only set if `is_authed` is FALSE). HTTP status code.
- `message`: character. Optional (typically only set if `is_authed` is FALSE). Longer description.

Currently, the `plumber` package does not support imposing filters on individual endpoints (but it is on the developer team's radar, see [this issue](https://github.com/trestletech/plumber/issues/108) :)). That makes
it difficult to require different levels of authorization, e.g. specific authorization for specific endpoints using the plumber filter method (see [jwt_claims_example](https://github.com/jandix/sealr/tree/master/examples/jwt/jwt_claims_example)).  

As a workaround, you can put your authentication / authorization checks in the individual endpoints.
The `is_authed_*` functions are designed so that you can use them independently from plumber filters as long 
as you pass a plumber request and response object. 

## Installation

Currently, the package is under development. Please feel free to contribute to the package. You can install and use the package using `devtools`. 

```{r installation, eval=FALSE}
devtools::install_github("jandix/sealr")
```

## Contribute

We are still at the very beginning of the package and we welcome any support and contribution. Below you find a list with possible authentication strategies that you could implement. The list is not complete and can be expanded with your suggestions. 

#### Possible Strategies

- [ ] Bearer Token
- [ ] Sessions
- [ ] Twitter OAuth
- [ ] Facebook OAuth
- [ ] Google OAuth

## Testing

You can use curl for testing purposes. Unfortunately, curl quickly gets quite complicated if you want to add a body, parameters and unique headers. Therefore, we recommend to use [Postman](https://www.getpostman.com/) for larger, more complicated projects. 

## Examples
We provide some simple sample implementations for different strategies and use cases. 
You can find them in the `examples` folder. 

## Warranity Notice

THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE SOFTWARE.


