---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# JWT Simple Example 

## Install the packages
Install the following packages if you haven't already:

- sealr
- httr
- jose
- jsonlite

## Run plumber

Source `jwt_simple_example.R` in your R session. This will make the API available at `localhost:9090`.

## Make some requests 

### Authentication route 

Using curl, Postman or a similar tool for sending HTTP requests, send a POST request with the details of one of the two users that are in the API's "database" (in this simplified example, a data frame).


```{r echo=FALSE}
users <- data.frame(id       = integer(),
                    name     = character(),
                    password = character(),
                    stringsAsFactors = FALSE)

# create test user
users <- rbind(users, data.frame(id       = 1,
                                 user     = "jane@example.com",
                                 password = bcrypt::hashpw("12345"),
                                 stringsAsFactors = FALSE))
users <- rbind(users, data.frame(id       = 2,
                                 user     = "bob@example.com",
                                 password = bcrypt::hashpw("45678"),
                                 stringsAsFactors = FALSE))
kableExtra::kable(users, format = "markdown")
```

For example, in curl: 

```
curl --data '{"user": "jane@example.com", "password": "12345"}' localhost:9090/authentication
```

gives back the JWT:

```
["eyJ0eXAiOiJKV1QiLCJhbGciOiJIUzI1NiJ9.eyJpYXQiOjE1NTE0NDk5NTcsInVzZXJJRCI6MX0.0563N-dcz9zY-NF9DQpUnHIONZRWmZU1rb894xxHcNU"]
```

Trying to authenticate with a user that is not in the database fails: 
```
curl --data '{"user": "drake@example.com", "password": "10111213"}' localhost:9090/authentication
```

```
{"status":["Failed."],"code":[401],"message":["User or password wrong."]}
```

### Routes with and without authentication 

Everyone can access the `/` route because it does not require authentication - the `sealr-jwt` filter is `preempt`ed for this route:
```
curl localhost:9090
```
This request gives back the first 100 rows of the iris dataset. 

Trying to access the `/secret` route without a JWT fails because it goes through the `sealr-jwt` filter where the `sealr::jwt` function will check for the correct authentication details - in this case a valid JWT in the Authorization header. 

```
curl localhost:9090/secret
```

```
{"status":["Failed."],"code":[401],"message":["Authentication required."]}
```

Use the JWT obtained with the first curl command to make an authenticated request to this route.

```
curl -H "Authorization: Bearer eyJ0eXAiOiJKV1QiLCJhbGciOiJIUzI1NiJ9.eyJpYXQiOjE1NTE0NDk5NTcsInVzZXJJRCI6MX0.0563N-dcz9zY-NF9DQpUnHIONZRWmZU1rb894xxHcNU localhost:9090/secret
```
This request gives back rows 100-150 of the iris dataset.

