---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# JWT Simple Example 

## JSON Web Tokens
"JSON Web Tokens are an open, industry standard RFC 7519 method for representing claims securely between two parties." (jwt.io)

The JWT stratgey allows to use JSON Web Tokens (JWT) to secure your plumber endpoints. A great introduction to JWT can be found [here](https://jwt.io/introduction/). JWT can be used to secure REST APIs without sessions. They are considered to be stateless. In `jwt_simple_example.R`, you find a small example of how to implement a JWT strategy in your application.  

The application consists of three routes. The first route allows your users to login and issues a JWT. The second route is an open route that does not require authentication. The third route requires authentication using the JWT.

The JWT filter looks like this:

```{r JWT strategy, eval=FALSE}
# integrate the jwt strategy in a filter
pr$filter("sealr-jwt", function (req, res) {
  # simply call the strategy and forward the request and response
  # please change the secret
  sealr::authenticate(req = req, res = res, is_authed_fun = is_authed_jwt, secret = "3ec9aaf4a744f833e98c954365892583")
})
```

:warning: Please change the secret to a super secure secret of your choice. Please notice that you have to `preempt = c("sealr-jwt")` to routes that should **not** be protected.

## Install the packages
Install the following packages if you haven't already:

- sealr
- httr
- jose
- jsonlite

## Run plumber

Source `jwt_simple_example.R` in your R session. This will make the API available at `localhost:9090`.

## Make some requests 

### Authentication route 

Using curl, Postman or a similar tool for sending HTTP requests, send a POST request with the details of one of the two users that are in the API's "database" (in this simplified example, a data frame).


```{r echo=FALSE}
users <- data.frame(id       = integer(),
                    name     = character(),
                    password = character(),
                    stringsAsFactors = FALSE)

# create test user
users <- rbind(users, data.frame(id       = 1,
                                 user     = "jane@example.com",
                                 password = bcrypt::hashpw("12345"),
                                 stringsAsFactors = FALSE))
users <- rbind(users, data.frame(id       = 2,
                                 user     = "bob@example.com",
                                 password = bcrypt::hashpw("45678"),
                                 stringsAsFactors = FALSE))
kableExtra::kable(users, format = "markdown")
```

For example, in curl: 

**Note**: You might get different JWTs as `jose::jwt_encode_hmac` automatically adds the time when the JWT was issued as a claim (`iat` claim). However, those examples should still work because we do not add an expiration time to the token -  something you should definetely consider for production use cases.  

```
curl --data '{"user": "jane@example.com", "password": "12345"}' localhost:9090/authentication
```

gives back the JWT:

```
["eyJ0eXAiOiJKV1QiLCJhbGciOiJIUzI1NiJ9.eyJpYXQiOjE1NTE0NDk5NTcsInVzZXJJRCI6MX0.0563N-dcz9zY-NF9DQpUnHIONZRWmZU1rb894xxHcNU"]
```

Trying to authenticate with a user that is not in the database fails: 
```
curl --data '{"user": "drake@example.com", "password": "10111213"}' localhost:9090/authentication
```

```
{"status":["Failed."],"code":[401],"message":["User or password wrong."]}
```

### Routes with and without authentication 

Everyone can access the `/` route because it does not require authentication - the `sealr-jwt` filter is `preempt`ed for this route:
```
curl localhost:9090
["Access to route without authentication was successful."]
```

Trying to access the `/secret` route without a JWT fails because it goes through the `sealr-jwt` filter where the `sealr::jwt` function will check for the correct authentication details - in this case a valid JWT in the Authorization header. 

```
curl localhost:9090/secret
```

```
{"status":["Failed."],"code":[401],"message":["Authentication required."]}
```

Use the JWT obtained with the first curl command to make an authenticated request to this route.

```
curl -H "Authorization: Bearer eyJ0eXAiOiJKV1QiLCJhbGciOiJIUzI1NiJ9.eyJpYXQiOjE1NTE0NDk5NTcsInVzZXJJRCI6MX0.0563N-dcz9zY-NF9DQpUnHIONZRWmZU1rb894xxHcNU" localhost:9090/secret
["Access to route requiring authentication was successful."]
```

